---
title: "Report - Nucleoplot"
author: "User"
date: Sys.Date()
output:
  rmarkdown::html_document:    
    theme: cayman
graphics: yes
---
```{r set-options, echo=FALSE, cache=FALSE}
options(width = 120)
```
### 1. Input sequences.
#### 1.1 Reference sequence.

```{r, echo= FALSE}
f_reference()$file_ref
```

#### 1.2 Problem sequences.

```{r, echo= FALSE}
f_problem()
```

### 2. CpG and GpC sites of reference sequence.

#### 2.1 CpG sites

```{r, echo= FALSE}
f_reference()$CpGsites
```

#### 2.2 GpC sites

```{r, echo= FALSE}
f_reference()$GpCsites
```


### 3. Quality control.

#### 3.1 Datatable information

```{r, echo= FALSE}
qc_sequences()[[1]]
```

#### 3.2 Quality control - sequences converted.

```{r, echo= FALSE}
qc_sequences()[[2]]
```

#### 3.3 Quality control - trimming sequences.

```{r, echo= FALSE}
choose_option()
```


### 4. Binaries datatables.

#### 4.1 Endogenous methylation (CpG sites).

```{r, echo= FALSE}
align_sequences()$END
```

#### 5.1 Endogenous methylation (GpC sites).

```{r, echo= FALSE}
align_sequences()$EXO
```

### 6. Clustering of sequences.

#### 6.1 Order sequences

```{r, echo= FALSE, , fig.align = "center"}
resume_df()
```


#### 6.2 Dendrogram hierachical clustering

```{r, echo= FALSE, , fig.align = "center"}
plot(df_clustering()[[3]])
```



### 7. Data analyses.

#### 7.1 Endogenous methylation (CpG sites)

##### 7.1.1 % Methylated

```{r, echo= FALSE, , fig.align = "center"}
nucleoplot_plot1()
```

#### 7.2 Exogenous methylation (GpC sites)

##### 7.2.1 % Methylated

```{r, echo= FALSE, fig.align = "center"}
nucleoplot_plot2()
```

##### 7.2.2 Nucleosome occupancy (% of unmethilated)

```{r, echo= FALSE, , fig.align = "center"}
nucleoplot_plot3()
```
