---
title: "NOMePlot - A Webtool for the analysis of bisulfite data PRUEBAAA"
graphics: yes
date: '`r Sys.Date()`'
output:
  html_document:
    fig_caption: yes
    highlight: tango
    theme: united
    toc: yes
    toc_depth: 3
subtitle: Technical report
---

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 120)
```
### 1. Input sequences.
#### 1.1 Reference genomic sequence.

```{r, echo= FALSE}
f_reference()$file_ref
```

#### 1.2 NOMe-treated sequences.

```{r, echo= FALSE}
f_problem()
```

### 2. CpG of reference genomic sequence.

#### 2.1 CpG sites

```{r, echo= FALSE}
f_reference()$CpGsites
```


### 3. Quality control.

#### 3.1 Datatable information

```{r, echo= FALSE}
qc_sequences()[[1]]
```

#### 3.2 Quality control - sequences converted.

```{r, echo= FALSE}
qc_sequences()[[2]]
```

#### 3.3 Quality control - trimming sequences.

```{r, echo= FALSE}
choose_option()
```


### 4. Binaries datatables.

#### 4.1 Endogenous methylation (CpG sites).

```{r, echo= FALSE}
align_sequences()$END
```

### 6. Clustering of sequences.

#### 6.1 Order of sequences

```{r, echo= FALSE, , fig.align = "center"}
resume_df()
```


#### 6.2 Dendrogram hierachical clustering

```{r, echo= FALSE, , fig.align = "center"}
plot(df_clustering()[[3]])
```
